---
title: "Model output and plots"
author: "Marina Espinasse and Sara Rutten"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: show
    toc: true
    toc_depth: 2
    toc_float: yes
    number_sections: true
    theme: cerulean
    highlight: pygments
  pdf_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

In this code, I will analyze model output for the selected model (bc_ozone_vaccine). I will plot the random effects, and the plots of lagged effects and main effects of ozone, bc, and vaccine.

# Lag-response and exposure-response effects form no-interaction model


Call the selected model - Base + BC + Ozone + vaccine

```{r}
load("output/models/model.bc_ozone_vaccine.RData")

source(knitr::purl("04_crossbasis_definition.rmd", quiet=TRUE))
#source("04_crossbasis_definition.R")

```


## Generate the predictions from DLNM

Here, coef is a list of effects' coefficients for all the basis functions in the model. Below, we extract coefficients only for a particular pollutant, using "grep" function. For example, basis functions associated with bc, are listed as 2nd to 10th.

```{r}
#Extract full coef and vcov and create indicators for each term
coef <- model$summary.fixed$mean
vcov <- model$misc$lincomb.derived.covariance.matrix
```

## The  effects of Black Carbon

First, we extract the effect of BC and then estimate predictions. 

```{r}
#find position of the terms associated with BC crossbasis
indt <- grep("basis_bc", model$names.fixed)

# extract predictions from the BC DLNM, center prediction on the minimal observed BC pollution  (0.06 mg/m3)
predt_bc <- crosspred(basis_bc, coef = coef[indt], vcov=vcov[indt,indt],
                   model.link = "log", bylag = 0.5, cen=round(min(data_sort$pollution_bc_wk), 2))
```

Here matRRfit is the matrix of exponentiated specific associations from matfit. As a result, we get relative risk (times increase/decrease in the risk of COVID-19).

y = predvar  is the vector or matrix of values used for predictions


```{r}
# contour plot of exposure-lag-response associations 
pdf("figs/bc_contour.pdf", width = 8, height = 6)

par(mar=c(5.1, 5, 4.1, 2.1))

y <- predt_bc$predvar
x <- seq(0, nlag, 0.5)
z <- t(predt_bc$matRRfit)

pal <- brewer.pal(9, "Purples")
levels <- pretty(z, 20)
col1 <- colorRampPalette(pal[2:9])
col2<-colorRampPalette(c("white", "grey90"))#grey palette for RR <1
cols_test <- c(col2(sum(levels < 1)), col1(sum(levels > 1)))
cols_test[c(1,2)] <- "#ffffff" #if you want to remove green for RR <1



filled.contour(x,y,z,
               xlab = "Lag, weeks", ylab = expression(paste("BC", " " ,"µg"/"m"^3)), main = "",
               col = cols_test,levels = levels,
               plot.axes = { axis(1, at = 0:nlag, c(0:nlag)) 
                 axis(2)})

#mtext(side = 4, at = max(y), text = "RR", las = 2, cex = 1.2, line = 2)

dev.off()
```



Lagged effects per level of BC

```{r}
# lag response for different BC scenarios: median pollution and maximal pollution
pdf("figs/bc_scenario.pdf", width = 6, height = 6)

# get exposures values
vars <- predt_bc$predvar

# obtain relative risk (RR) fit and upper and lower confidence limits for all exposure variables
rr <- predt_bc$matRRfit
rr.lci <- predt_bc$matRRlow
rr.uci <- predt_bc$matRRhigh

# set relative risk range 
r1 <- min(range(rr, rr.lci, rr.uci))
r2 <- max(range(rr, rr.lci, rr.uci))

# get selected exposure variable positions
md <- which(round(vars, 2) == 0.4)
mx <- which(round(vars, 2) == 1.7)


# define colours
col1 <- brewer.pal(9, "Purples")[4]
tcol1 <- do.call(rgb, c(as.list(col2rgb(col1)), alpha = 255/4, max = 255))

col2 <- brewer.pal(9, "Purples")[9]
tcol2 <- do.call(rgb, c(as.list(col2rgb(col2)), alpha = 255/4, max = 255))


# define x values (lag, by lag)
lagbylag <- seq(0, nlag, 0.5)

# median pollution
plot(lagbylag, rr[md,], col = col1, type = "l", lwd = 1, 
     xlab = "Lag, weeks", ylab = "RR", main = "", 
     ylim = c(0.8,2.3), frame.plot = T, axes = F)
axis(1, at = 0:nlag, labels = 0:nlag)
axis(2)
xx <- c(lagbylag, rev(lagbylag))
yy <- c(rr.lci[md,], rev(rr.uci[md,]))
polygon(xx, yy, col = tcol1, border = tcol1)


# maximal pollution
lines(lagbylag, rr[mx,], col = col2, lwd = 1)
xx <- c(lagbylag, rev(lagbylag))
yy <- c(rr.lci[mx,], rev(rr.uci[mx,]))
polygon(xx, yy, col = tcol2, border = tcol2)
abline(h = 1, lty = 3)

#expression(paste("BC", " " ,"µg"/"m"^3))
legend("topleft",
       legend = c(expression(paste("BC = ","0.4"," ", "µg"/"m"^3)),
                      expression(paste("BC = ","1.7"," ", "µg"/"m"^3))      ),
       col = c(col1, col2), cex = 0.8,
       lwd = 2, lty = 1, bty = "n", 
       y.intersp = 1.2, horiz = F)

#mtext(side = 2, at = r2*1.25, text = "b", las = 2, cex = 1.2, line = 2)

dev.off()
```


## The effects of Ozone


```{r}
#find position of the terms associated with ozone crossbasis
indt <- grep("basis_ozone", model$names.fixed)

# extract predictions from the  DLNM, center prediction on the minimal observed  pollution  (6.757 mg/m3)
predt_ozone <- crosspred(basis_ozone, coef = coef[indt], vcov=vcov[indt,indt],
                   model.link = "log", bylag = 0.5, cen=round(min(data_sort$pollution_ozone_wk), 2))
```


All the same plots as for black carbon will be made for ozone

```{r}
pdf("figs/ozone_contour.pdf", width = 8, height = 6)

par(mar=c(5.1, 5, 4.1, 2.1))

y <- predt_ozone$predvar
x <- seq(0, nlag, 0.5)
z <- t(predt_ozone$matRRfit)

pal <- brewer.pal(9, "Reds")
levels <- pretty(z, 20)
col1 <- colorRampPalette(pal[2:9])
col2<-colorRampPalette(c("white", "grey90"))#grey palette for RR <1
cols_test <- c(col2(sum(levels < 1)), col1(sum(levels > 1)))
cols_test[c(1,2,3)] <- "#ffffff" #if you want to remove green for RR <1



filled.contour(x,y,z,
               xlab = "Lag, weeks", ylab = expression(paste("Ozone", " " ,"µg"/"m"^3)), main = "",
               col = cols_test,levels = levels,
               plot.axes = { axis(1, at = 0:nlag, c(0:nlag)) 
                 axis(2)})


dev.off()
```

Scenario for median and close to maximal ozone levels

```{r}
# lag response for different ozone scenarios: median pollution and maximal pollution
pdf("figs/ozone_scenario.pdf", width = 6, height = 6)

# get exposures values
vars <- predt_ozone$predvar

# obtain relative risk (RR) fit and upper and lower confidence limits for all exposure variables
rr <- predt_ozone$matRRfit
rr.lci <- predt_ozone$matRRlow
rr.uci <- predt_ozone$matRRhigh

# set relative risk range 
r1 <- min(range(rr, rr.lci, rr.uci))
r2 <- max(range(rr, rr.lci, rr.uci))

# get selected exposure variable positions
md <- which(round(vars, 2) == 46)
mx <- which(round(vars, 2) == 76)


# define colours
col1 <- brewer.pal(9, "Reds")[4]
tcol1 <- do.call(rgb, c(as.list(col2rgb(col1)), alpha = 255/4, max = 255))

col2 <- brewer.pal(9, "Reds")[9]
tcol2 <- do.call(rgb, c(as.list(col2rgb(col2)), alpha = 255/4, max = 255))


# define x values (lag, by lag)
lagbylag <- seq(0, nlag, 0.5)

# median pollution
plot(lagbylag, rr[md,], col = col1, type = "l", lwd = 1, 
     xlab = "Lag, weeks", ylab = "RR", main = "", 
     ylim = c(0.8,3), frame.plot = T, axes = F)
axis(1, at = 0:nlag, labels = 0:nlag)
axis(2)
xx <- c(lagbylag, rev(lagbylag))
yy <- c(rr.lci[md,], rev(rr.uci[md,]))
polygon(xx, yy, col = tcol1, border = tcol1)


# maximal pollution
lines(lagbylag, rr[mx,], col = col2, lwd = 1)
xx <- c(lagbylag, rev(lagbylag))
yy <- c(rr.lci[mx,], rev(rr.uci[mx,]))
polygon(xx, yy, col = tcol2, border = tcol2)
abline(h = 1, lty = 3)

legend("topleft",
       legend = c(expression(paste("Ozone = ","46"," ", "µg"/"m"^3)),
                      expression(paste("Ozone = ","76"," ", "µg"/"m"^3)) ),
       col = c(col1, col2), cex = 0.8,
       lwd = 2, lty = 1, bty = "n", 
       y.intersp = 1.2, horiz = F)

#mtext(side = 2, at = r2*1.25, text = "b", las = 2, cex = 1.2, line = 2)

dev.off()
```
## The effects of vaccine

This plots was just a check of vaccine effects

```{r}
#find position of the terms associated with vaccine crossbasis
indt <- grep("basis_vaccine", model$names.fixed)

# extract predictions from the DLNM, center prediction on the minimal vaccine level (0)
predt_vaccine <- crosspred(basis_vaccine, coef = coef[indt], vcov=vcov[indt,indt],
                   model.link = "log", bylag = 0.5, cen = max(data_prep$vaccine_rate))
```


All the same plots as for vaccine

```{r}
pdf("figs/vaccine_contour.pdf", width = 8, height = 6)

par(mar=c(5.1, 5, 4.1, 2.1))

y <- predt_vaccine$predvar
x <- seq(0, 2, 0.5)
z <- t(predt_vaccine$matRRfit)

pal <- brewer.pal(9, "Blues")
levels <- pretty(z, 20)
col1 <- colorRampPalette(pal[2:9])
col2<-colorRampPalette(c("white", "grey90"))#grey palette for RR <1
cols_test <- c(col2(sum(levels < 1)), col1(sum(levels > 1)))
#cols_test[c(1,2,3)] <- "#ffffff" #if you want to remove green for RR <1



filled.contour(x,y,z,
               xlab = "Lag, weeks", ylab = "vaccine", main = "",
               col = cols_test,levels = levels,
               plot.axes = { axis(1, at = 0:2, c(0:2)) 
                 axis(2)})


dev.off()
```

Scenario for median and close to maximal vaccine levels

```{r}
# lag response for different vaccine scenarios: median and maximal vaccination
pdf("figs/vaccine_scenario.pdf", width = 6, height = 6)

# get exposures values
vars <- predt_vaccine$predvar

# obtain relative risk (RR) fit and upper and lower confidence limits for all exposure variables
rr <- predt_vaccine$matRRfit
rr.lci <- predt_vaccine$matRRlow
rr.uci <- predt_vaccine$matRRhigh

# set relative risk range 
r1 <- min(range(rr, rr.lci, rr.uci))
r2 <- max(range(rr, rr.lci, rr.uci))

# get selected exposure variable positions
md <- which(round(vars, 2) == 70)
mx <- which(round(vars, 2) == 30)


# define colours
col1 <- brewer.pal(9, "Blues")[4]
tcol1 <- do.call(rgb, c(as.list(col2rgb(col1)), alpha = 255/4, max = 255))

col2 <- brewer.pal(9, "Blues")[9]
tcol2 <- do.call(rgb, c(as.list(col2rgb(col2)), alpha = 255/4, max = 255))


# define x values (lag, by lag)
lagbylag <- seq(0, 2, 0.5)

# median vaccination
plot(lagbylag, rr[md,], col = col1, type = "l", lwd = 1, 
     xlab = "Lag, weeks", ylab = "RR", main = "", 
     ylim = range(r1, r2*1.11), frame.plot = T, axes = F)
axis(1, at = 0:2, labels = 0:2)
axis(2)
xx <- c(lagbylag, rev(lagbylag))
yy <- c(rr.lci[md,], rev(rr.uci[md,]))
polygon(xx, yy, col = tcol1, border = tcol1)


# maximal vaccination
lines(lagbylag, rr[mx,], col = col2, lwd = 1)
xx <- c(lagbylag, rev(lagbylag))
yy <- c(rr.lci[mx,], rev(rr.uci[mx,]))
polygon(xx, yy, col = tcol2, border = tcol2)
abline(h = 1, lty = 3)

legend("topleft",
       legend = c(expression(paste("vaccine = ","70"," ", "µg"/"m"^3)),
                      expression(paste("vaccine = ","30"," ", "µg"/"m"^3))      ),
       col = c(col1, col2), cex = 0.8,
       lwd = 2, lty = 1, bty = "n", 
       y.intersp = 1.2, horiz = F)

#mtext(side = 2, at = r2*1.25, text = "b", las = 2, cex = 1.2, line = 2)

dev.off()
```


# BC: Cumulative effect of pollution

We again load the selected model (unless it is already loaded)

```{r}
load("output/models/model.bc_ozone_vaccine.RData")
```

```{r}
#Extract full coef and vcov and create indicators for each term
coef <- model$summary.fixed$mean
vcov <- model$misc$lincomb.derived.covariance.matrix
```

```{r}
#find position of the terms associated with BC crossbasis
indt <- grep("basis_bc", model$names.fixed)

# extract predictions from the BC DLNM, center prediction on the minimal observed BC pollution  (0.06 mg/m3)
predt_bc <- crosspred(basis_bc, coef = coef[indt], vcov=vcov[indt,indt],
                   model.link = "log", bylag = 0.5, cen = round(min(data_sort$pollution_bc_wk), 2), cumul = TRUE)
```

## Plot for cumulative effects

For the following plot, I will also add the quantiles of BC concentrations used for predictions: 
20% = 0.27, 50% =0.44,  95% = 1.2.

```{r}
pdf("figs/bc_cumul_contour.pdf", width = 8, height = 6)
plot(predt_bc, ptype="overall",  xlab = expression(paste("BC", " " ,"µg"/"m"^3)), ylab="RR", col=6, ylim=c(0,100),
     xlim=c(0,2.2))
abline(v=0.27, col="slateblue4", lty = 3, lwd = 2)#20%
abline(v=0.44, col="slateblue4", lty = 3, lwd = 2)#50%
abline(v=1.2, col="slateblue4", lty = 3, lwd = 2)#95%
text(0.27, 50,col="slateblue4", "20%", cex = 1)
text(0.44, 50,col="slateblue4", "50%", cex = 1)
text(1.2, 50,col="slateblue4", "95%", cex = 1)
```


# Ozone: Cumulative effect of pollution


```{r}
#find position of the terms associated with BC crossbasis
indt <- grep("basis_ozone", model$names.fixed)

# extract predictions from the BC DLNM, center prediction on the minimal observed BC pollution  (0.06 mg/m3)
predt_ozone <- crosspred(basis_ozone, coef = coef[indt], vcov=vcov[indt,indt],
                   model.link = "log", bylag = 0.5, cen = round(min(data_sort$pollution_ozone_wk), 2), cumul = TRUE)
```

Quantiles of ozone pollution 20% = 31.7, 50% = 45.8 , 95% = 69.9

```{r}
pdf("figs/ozone_cumul_contour.pdf", width = 8, height = 6)
plot(predt_ozone,col="red", ptype="overall", xlab=expression(paste("Ozone", " " ,"µg"/"m"^3)), ylab="RR", main="", ylim = c(0,100)) 
abline(v=31.7, col="red4", lty = 3, lwd = 2)#20%
abline(v=45.8, col="red4", lty = 3, lwd = 2)#50%
abline(v=69.9, col="red4", lty = 3, lwd = 2)#95%
text(31.7, 50,col="red4", "20%", cex = 1)
text(45.8, 50,col="red4", "50%", cex = 1)
text(69.9, 50,col="red4", "95%", cex = 1)
```


# vaccine: Cumulative effect of pollution


```{r}
#find position of the terms associated with BC crossbasis
indt <- grep("basis_vaccine", model$names.fixed)

# extract predictions from the BC DLNM, center prediction on the minimal observed BC pollution  (0.06 mg/m3)
predt_vaccine <- crosspred(basis_vaccine, coef = coef[indt], vcov=vcov[indt,indt],
                   model.link = "log", bylag = 0.5, cen = max(data_prep$vaccine_rate), cumul = TRUE)
```

```{r}
pdf("figs/vaccine_cumul_contour.pdf", width = 8, height = 6)
plot(predt_vaccine,col="green4", ptype="overall", xlab="vaccination rate", ylab="RR", main="", ylim = c(0,10)) 
abline(v=0, col="green4", lty = 3, lwd = 2)#20%
abline(v=15.8, col="green4", lty = 3, lwd = 2)#50%
abline(v=83.93, col="green4", lty = 3, lwd = 2)#95%
text(0, 8,col="green4", "20%", cex = 1)
text(15.8, 8,col="green4", "50%", cex = 1)
text(83.93, 8,col="green4", "95%", cex = 1)
```

