---
title: "Running and comparing INLA models"
author: "Marina Espinasse and Sara Rutten"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: show
    toc: true
    toc_depth: 2
    toc_float: yes
    number_sections: true
    theme: cerulean
    highlight: pygments
  pdf_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```


# Poisson model

```{r}
source(knitr::purl("04_crossbasis_definition_poisson.rmd", quiet=TRUE)) #use when running for the 1st time
#source("04_crossbasis_definition.R")
```

```{r}
baseformula <- Y ~ f(T1,  model = "rw2", constr = TRUE, scale.model = TRUE, hyper = precision.prior) +
  f(S1, model = "bym2",graph = "../output/adjacency.mat", scale.model = TRUE, hyper = precision.prior)

formula.ozone <- update.formula(baseformula, ~ . + basis_ozone + basis_vaccine)
formula.no2 <- update.formula(baseformula, ~ . + basis_no2 + basis_vaccine)
formula.pm10 <- update.formula(baseformula, ~ . + basis_pm10 + basis_vaccine)
formula.pm25 <- update.formula(baseformula, ~ . + basis_pm25 + basis_vaccine)
formula.bc <- update.formula(baseformula, ~ . + basis_bc + basis_vaccine)
formula.vaccine <- update.formula(baseformula, ~ . + basis_vaccine)
```


```{r}
formulas <- list(formula.ozone, formula.no2, formula.pm10, formula.pm25, formula.bc, formula.vaccine)
labels <- c("model.ozone", "model.no2", "model.pm10", "model.pm25", "model.bc", "model.vaccine")
```

Run all models and extract DIC, save the model output 

```{r}
models <- lapply(1:length(formulas), 
              function(i) {
                model <- mymodel(formulas[[i]], df)
                save(model, file = paste0("../output/models/Poisson/", labels[i],".RData"))})
```

# Calculate the model comparison diagnostics
log CPO = conditional predictive ordinate
DIC 

```{r}
table0 <- data.table::data.table(Model  = c("ozone", "no2", "pm10", "pm25", "bc", "vaccine"),
                     DIC = NA, logCPO = NA)

for(i in 1:length(formulas))
  {
  load(paste0("../output/models/Poisson/",labels[i],".RData"))
  table0$DIC[i] <- round(model$dic$dic, 0)
  table0$logCPO[i] <- round(-mean(log(model$cpo$cpo), na.rm=T), 4)
 # gcpo = inla.group.cv(model,  groups = groups, strategy = "posterior")
 # table0$logGCPO[i] <- round(-mean(log(gcpo$cv), na.rm=T), 4)
}

# view table
table0
```



# Linear exposure

```{r}
source(knitr::purl("04_crossbasis_definition_linear_exposure.rmd", quiet=TRUE)) #use when running for the 1st time
#source("04_crossbasis_definition.R")
```

```{r}
baseformula <- Y ~ f(T1,  model = "rw2", constr = TRUE, scale.model = TRUE, hyper = precision.prior) +
  f(S1, model = "bym2",graph = "../output/adjacency.mat", scale.model = TRUE, hyper = precision.prior)

formula.ozone <- update.formula(baseformula, ~ . + basis_ozone + basis_vaccine)
formula.no2 <- update.formula(baseformula, ~ . + basis_no2 + basis_vaccine)
formula.pm10 <- update.formula(baseformula, ~ . + basis_pm10 + basis_vaccine)
formula.pm25 <- update.formula(baseformula, ~ . + basis_pm25 + basis_vaccine)
formula.bc <- update.formula(baseformula, ~ . + basis_bc + basis_vaccine)
```


```{r}
formulas <- list(formula.ozone, formula.no2, formula.pm10, formula.pm25, formula.bc)
labels <- c("model.ozone", "model.no2", "model.pm10", "model.pm25", "model.bc")
```

Run all models and extract DIC, save the model output 

```{r}
models <- lapply(1:length(formulas), 
              function(i) {
                model <- mymodel(formulas[[i]], df)
                save(model, file = paste0("../output/models/Linear exposure/", labels[i],".RData"))})
```


# Linear lag

```{r}
source(knitr::purl("04_crossbasis_definition_linear_lag.rmd", quiet=TRUE)) #use when running for the 1st time
#source("04_crossbasis_definition.R")
```

```{r}
baseformula <- Y ~ f(T1,  model = "rw2", constr = TRUE, scale.model = TRUE, hyper = precision.prior) +
  f(S1, model = "bym2",graph = "../output/adjacency.mat", scale.model = TRUE, hyper = precision.prior)

formula.ozone <- update.formula(baseformula, ~ . + basis_ozone + basis_vaccine)
formula.no2 <- update.formula(baseformula, ~ . + basis_no2 + basis_vaccine)
formula.pm10 <- update.formula(baseformula, ~ . + basis_pm10 + basis_vaccine)
formula.pm25 <- update.formula(baseformula, ~ . + basis_pm25 + basis_vaccine)
formula.bc <- update.formula(baseformula, ~ . + basis_bc + basis_vaccine)
```


```{r}
formulas <- list(formula.ozone, formula.no2, formula.pm10, formula.pm25, formula.bc)
labels <- c("model.ozone", "model.no2", "model.pm10", "model.pm25", "model.bc")
```

Run all models and extract DIC, save the model output 

```{r}
models <- lapply(1:length(formulas), 
              function(i) {
                model <- mymodel(formulas[[i]], df)
                save(model, file = paste0("../output/models/Linear lag/", labels[i],".RData"))})
```



# Additional covariates

```{r}
source(knitr::purl("04_crossbasis_definition_additional_covariates.rmd", quiet=TRUE)) #use when running for the 1st time
#source("04_crossbasis_definition.R")
```

```{r}
baseformula <- Y ~ f(T1,  model = "rw2", constr = TRUE, scale.model = TRUE, hyper = precision.prior) +
  f(S1, model = "bym2",graph = "../output/adjacency.mat", scale.model = TRUE, hyper = precision.prior)

formula.ozone <- update.formula(baseformula, ~ . + basis_ozone + basis_vaccine)
formula.no2 <- update.formula(baseformula, ~ . + basis_no2 + basis_vaccine)
formula.pm10 <- update.formula(baseformula, ~ . + basis_pm10 + basis_vaccine)
formula.pm25 <- update.formula(baseformula, ~ . + basis_pm25 + basis_vaccine)
formula.bc <- update.formula(baseformula, ~ . + basis_bc + basis_vaccine)
```


```{r}
formulas <- list(formula.ozone, formula.no2, formula.pm10, formula.pm25, formula.bc)
labels <- c("model.ozone", "model.no2", "model.pm10", "model.pm25", "model.bc")
```

Run all models and extract DIC, save the model output 

```{r}
models <- lapply(1:length(formulas), 
              function(i) {
                model <- mymodel(formulas[[i]], df)
                save(model, file = paste0("../output/models/Additional covariates/", labels[i],".RData"))})
```


